A Systematic Literature Review on Role-Based Access Control

### 2013-02-05 paper/sections/intro.tex
Some minor updates and the start of a data extraction section.

Role-based access control (RBAC) models {\hyperref[intro:ferraiolo-rbac]{{[}1{]}}} become popularly used to govern access to critical resources.  In an RBAC model, roles represent a group of users who are involved in a specific job function in an organization. RBAC assigns permissions of specific actions on resources to roles instead of individual users.  Therefore, in order to gain roles' permission on specific resources, users acquire appropriate roles first.

@@

RBAC is first introduced in 1990s, NIST proposed standard RBAC model {\hyperref[intro:ferraiolo-rbac]{{[}1{]}}}
Standard RBAC model considers only role-user association and role hierarchy.
Since standard RBAC model has limitations such as specifying environmental constraints or context information
Researchers developed extended models of RBAC to overcome the limitations.
However, as researchers often develop their own specialized extended models of RBAC,
their research cannot be generalized or compared with other research work appropriately.
As a result, researchers could take time on reinventing the wheel.
But how do we, as a community, ensure that a metric is suitable and acceptable for its intended purpose?

>>>>

Role-based access control (RBAC) models \cite{ferraiolo-rbac} become popularly used to govern access to critical resources.  In an RBAC model, roles represent a group of users who are involved in a specific job function in an organization. RBAC assigns permissions of specific actions on resources to roles instead of individual users.  Therefore, in order to gain roles' permission on specific resources, users acquire appropriate roles first.

@@

RBAC is first introduced in 1990s, NIST proposed standard RBAC model \cite{ferraiolo-rbac}
Standard RBAC model considers only role-user association and role hierarchy.
Since standard RBAC model has limitations such as specifying environmental constraints or context information
Researchers developed extended models of RBAC to overcome the limitations.
However, as researchers often develop their own specialized extended models of RBAC,
their research cannot be generalized or compared with other research work appropriately.
As a result, researchers could take time on reinventing the wheel.
But how do we, as a community, ensure that a metric is suitable and acceptable for its intended purpose?

### 2013-02-05 paper/sections/process.tex
Some minor updates and the start of a data extraction section.

For the first phase of our systematic literature review, an automated comprehensive search of multiple academic search engines was performed. The list of search engines were:
\begin{itemize}
\item {} 
Google Scholar - \href{http://scholar.google.com}{http://scholar.google.com}
\item {} 
IEEExplore     - \href{http://ieeexplore.ieee.org}{http://ieeexplore.ieee.org}
\item {} 
ACM Portal     - \href{http://dl.acm.org}{http://dl.acm.org}
\item {} 
CiteSeerX      - \href{http://http://citeseerx.ist.psu.edu/index}{http://http://citeseerx.ist.psu.edu/index}
\end{itemize}

For each of the criteria below, a search was performed on each of the search engines for a total of 12 data sets.  The criteria used were:
\begin{itemize}
\item {} 
role based access control
\item {} 
RBAC
\item {} 
role-based access control
\end{itemize}

The search performed was done in an automated way using a set of scripts to query and collect data from each search engine with the criteria string as input.  For each criteria for each search engine, the results were captured until a stopping criteria was met.  Each run was performed as follows:
\begin{enumerate}
\item {} 
Remote call to search engine with current search start position and the current search criteria.
\item {} 
Parse results and extract paper title, authors and year of publication.
\item {} 
Compare results against stopping criteria.
\end{enumerate}

\begin{itemize}
\item {} 
If stopping criteria met, stop search.
\item {} 
If stopping criteria not met, increase search position by number of results and return to step 1.
\end{itemize}

@@

There were a total of three elimination rounds.  The first round was based solely on title, the second on reading of the abstract and the last round was based on a full read of the paper and comparison to the research questions outlined.  Each round was performed as follows:

\begin{itemize}
\item {} 
Each reviewer independently classified papers as relevant, irrelevant or uncertain.
\item {} 
Those papers marked as relevant by both reviewers were kept and those marked irrelevant by both were thrown out.
\item {} 
Papers marked as relevant, or irrelevant by a single reviewer were combined with all papers marked as uncertain and discussed by both reviewers.  From this discussion, papers were either thrown out or kept until the next round of the review.  Ties were broken by an indepedent party.
\end{itemize}

@@

\begin{tabulary}{\linewidth}{|L|L|L|L|L|}
\hline
\textbf{
Search Engines
} & \textbf{
RBAC
} & \textbf{
role based access control
} & \textbf{
role-based access control
} & \textbf{
Total
}\\\hline

@@

Combined
 &  &  &  & 
\textbf{1716}
\\\hline
\end{tabulary}

>>>>

The systematic literature review process was developed ahead of time and agreed upon by the researchers following recommendations from Kitchenham's suggested processes \cite{kitchenham2007guidelines}.  The systematic literature review was performed in four stages:

\begin{itemize}
\item Development of a search strategy
\item Elimination of papers based on title
\item Elimination of papers based on abstract
\item Elimination of papers based on content and matching to elimination criteria
\end{itemize}

\subsection{Search Strategy}

For the first phase of our systematic literature review, an automated comprehensive search of multiple academic search engines was performed. The list of search engines were:

\begin{itemize}
\item Google Scholar - \url{http://scholar.google.com}
\item IEEExplore - \url{http://ieeexplore.ieee.org}
\item ACM Portal - \url{http://dl.acm.org}
\item CiteSeerX - \url{http://http://citeseerx.ist.psu.edu/index}
\end{itemize}

For each of the criteria below, a search was performed on each of the search engines for a total of 12 data sets.  The criteria used were:
\begin{itemize}
\item role based access control
\item RBAC
\item role-based access control
\end{itemize}

The search performed was done in an automated way using a set of scripts to query and collect data from each search engine with the criteria string as input.  For each criteria for each search engine, the results were captured until a stopping criteria was met.  Each run was performed as follows:

\begin{enumerate}
\item Remote call to search engine with current search start position and the current search criteria.
\item Parse results and extract paper title, authors and year of publication.
\item Compare results against stopping criteria.
\end{enumerate}

\begin{itemize}
\item If stopping criteria met, stop search.
\item If stopping criteria not met, increase search position by number of results and return to step 1.
\end{itemize}

@@

\subsection{Elimination Rounds}

The elimination rounds were performed based on reading of the title, abstract and finally the paper itself.  While each elimination stage had a unique set of criteria for elimination the general procedure for elimination for the researchers was as follows.

\begin{itemize}
\item Each reviewer independently classified papers as relevant, irrelevant or uncertain.
\item Those papers marked as relevant by both reviewers were kept and those marked irrelevant by both were thrown out.
\item Papers marked as relevant, or irrelevant by a single reviewer were combined with all papers marked as uncertain and discussed by both reviewers.  From this discussion, papers were either thrown out or kept until the next round of the review.  Ties were broken by an indepedent party.
\end{itemize}

The title elimination round was based off of whether role based access control and model were mentioned directly.

The second round of elimination was based off on reading the abstracts of the remaining papers.  The inclusion criteria for the abstract reading tried to answer the following questions:

\begin{itemize}
\item Does the abstract mention a proposed model?
\item Does the abstract mention extension of role-based access control?
\item Does the abstract mention either an implementation, evaluation or domain for their model?
\end{itemize}

@@

\begin{tabular}{|l|l|l|l|l|}
\hline
\textbf{Search Engines} & 
\textbf{RBAC} & 
\textbf{role based access control} & 
\textbf{role-based access control} & 
\textbf{Total}
\\\hline

@@

Combined &  &  &  & \textbf{1716}
\\\hline
\end{tabular}
